---
title: "Generic Analysis Template"
author: "by [Cormac Nolan](https://github.com/cormac85/) - `r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    code_folding: "hide"
    css: style.css
    includes: 
      after_body: footer.html
      in_header: header.html
editor_options: 
  chunk_output_type: console
---

# LinkedIn {.tabset .tabset-fade .tabset-pills}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Blah
```{r libraries, message = FALSE, warning = FALSE}
library(tidyverse)
library(igraph)
```


```{r functions}

```


```{r import}
members_graph <- 
  read_csv("./linkedin_data/common_connection_200k.csv") %>% 
  sample_n(10000) %>% # take a sample
  graph_from_data_frame(directed = FALSE)

```

## Exploration
```{r raw exploration}
print("Number of vertices:")
vertex_attr(members_graph)$name %>% unique() %>% length()

```


```{r explo 1}
edges <- get.edgelist(members_graph) 

edges_df <-
  edges %>% 
  as.tibble() %>% 
  rename(member = V1, member_conn = V2)

edges_df %>% arrange(member, member_conn)

rm(edges)
```


```{r explo 2}

```

## Exploration
Algorithm in English:
1. Get Member
2. Get Member's Connection
3. For Each Connection, Get List of Connections Connections
4. Check If Connections Connections Are In Member's Connections
5. If Yes: Increment & Store Counter for Member vs Connections
6. Repeat 1-5 Until All Relationships of Friends of Friends Calculated

Number of unique member names vs total number of member names in sample:
```{r exploration 1}
edges_df$member %>% unique() %>% length()
edges_df$member %>% length()
```


```{r exploration 2}

```


```{r exploration 3}

```


```{r summary}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```
